---
output:
  md_document:
    variant: gfm
---
 
## KnowSeq Shiver: The Shiny Version of KnowSeq R/Bioc Package

*KnowSeq Shiver* is the shiny-based web application of the [KnowSeq R/Bioc package](https://github.com/CasedUgr/KnowSeq) that allows users with no previous knowledge of programming to analyze transcriptomics data using all the functionalities available at KnowSeq.

*KnowSeq Shiver* is currently available at [https://knowseqshiver.shinyapps.io/KnowSeq_Shiny/](https://knowseqshiver.shinyapps.io/KnowSeq_Shiny/)


## Citation
```
Castillo-Secilla, D., Gálvez, J. M., Carrillo-Pérez, F., Verona-Almeida, M., Redondo-Sánchez, D., Ortuno, F. M., Herrera, L. J. & Rojas, I. (2021). KnowSeq R-Bioc package: The automatic smart gene expression tool for retrieving relevant biological knowledge. Computers in Biology and Medicine, 133, 104387.
```


## Authors 

Daniel Castillo. University of Granada.

Juan Manuel Gálvez. University of Granada.

Francisco Carrillo-Pérez. University of Granada.

Marta Verona-Almeida. University of Granada.

Daniel Redondo-Sánchez. Granada Cancer Registry, ibs.GRANADA.

Francisco Manuel Ortuño. Fundación Progreso y Salud (FPS), Hospital Virgen del Rocio, Sevilla.

Luis Javier Herrera. University of Granada.

Ignacio Rojas. University of Granada.

## Contact

Daniel Castillo-Secilla (cased at ugr.es) is the main developer of the R package KnowSeq.

Daniel Redondo-Sánchez (daniel.redondo.easp at juntadeandalucia.es) is the main developer of this Shiny App.

## Session info

```{r, echo = FALSE, results=F, warning=F, message=F}
# Load all packages used in the Shiny app
# This won't appear in the README but is useful to display the version of the packages
library(KnowSeq)
library(waiter)
library(dplyr)
library(reshape2)
library(caret)
library(ggplot2)
library(ggalluvial)
library(waiter)
library(shinydashboard)
library(DT)
library(shiny)
library(BiocManager)
```

```{r sessionInfo, warning=F, message = F}
library(devtools)
devtools::session_info()
```